Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-07-23 document/ms.tex
Overhual the introduction, still in progress, add references

%Jackson \& Jeffries 2014ab needs to go somewhere.

Starspots have recently been observed with few parts per million photometric precision from monitoring surveys targeting exoplanet transits (Harrison, Davenport, etc.).  Contemporaneous or near-contemporaneous panchromatic photometric monitoring (Grankin, etc.) can break the degeneracy between starspot areal filling factor and starspot temperature. Photometric measurements are limited to detecting the largest longitudinally asymmetric starspots.  Transiting planets or eclipsing binaries passing in front of starspots (cite XX) can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups.  Zeeman Doppler Imaging (ZDI, cite XX) suffers from the same longitudinally-asymmetric limitation as photometry, but yields information on the latitudinal distribution of starspots.  All of these techniques would underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots (e.g. bands), or stars with an isotropic distribution of small starspots.

Spectroscopic strategies have the power to measure both the average areal coverage and the area-weighted average starspot temperature contrast in any geometric configuration.  At low resolution, SED modeling (Wolk and Walker) has detected evidence for sunspots in weak-lined T-Tauri stars (WTTS).  At high resolution, line depth ratio analysis (Neff, etc) has historically been demonstrated in isolated regions of spectrum, namely the TiO bands (cite O'Neal, Neff, etc), OH 1.5 micron feature (O'Neal, etc.), and others.

>>>>

% Theory of starspots
% Jackson \& Jeffries 2014ab needs to go somewhere.

Starspots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep{harrison11,davenport15}.  Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{bouvier95,grankin07} can break the degeneracy between starspot areal filling factor and starspot temperature. Photometric measurements are limited to detecting the largest longitudinally asymmetric starspots.  Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups.  Zeeman Doppler Imaging (ZDI, \emph{e.g.} \citet{donati14}) suffers from the same longitudinally-asymmetric limitation as photometry, but yields information on the latitudinal distribution of starspots.  All of these techniques would underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots (e.g. bands), or stars with an isotropic distribution of small starspots.

Spectroscopic strategies have the power to measure both the starspot areal coverage and temperature in any geometric configuration.  At low resolution, SED modeling \citep{wolk96} has detected evidence for sunspots in weak-lined T-Tauri stars (WTTS).  At high resolution, line depth ratio analysis has historically been demonstrated in relatively small bandwidths, namely the TiO bands \citep{neff95,oneal96,oneal98,oneal04}, or the OH 1.563 $\mu$m feature \citep{oneal01}.
